Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-12 WRITEUP/ms.tex
update MR relation caption

We show in \Fig{MR} the size-mass relation of the MCs of \flower in the accretion phase (see \Sec{sfh})
compared to the 
observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF 
\citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and the empirical relation obtained based on 
Milky Way data (\citealt{Kauffmann10b, Kauffmann10c} and references therein).
This relation is obtained by comparing the masses and sizes found in clouds with and without massive \SF ($<$10\,\Msun). 
\citet{Kauffmann10c} interpret this
mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as
the threshold for massive \SF.
The implication of this result is that cluster-forming cloud fragments are 
found to be more massive than those that are devoid of clusters 
at a given radius.

As shown in \Fig{MR}, the MCs identified in the accretion phase of \flower lie above this relation, along the locus 
with a visual extinction of $A_V$\eq4\,mag \citep{Lombardi10a}, which 
% {\AP note that we can directly calculate Av given the dust properties in the galaxy or approximate it as av = cost N * Z con cost assuming a MW-like scaling}
is below the locus of $A_V$\eq100\,mag followed by Milky Way clouds.
This can be understood by acknowledging the fact that a H$_2$ molecular cloud 
does not necessary contain CO (e.g., as CO forms deeper in molecular clouds),
and that our simulation does not have enough resolution to directly form CO\footnote{
In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we 
model the internal structure of MC within each cell in our simulation.}.
That is, the MCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the 
fact that the MCs in our simulation have lower column density compared to the star-forming cores observed in the Milky Way, which are 
observationally well-resolved within an MC, and indeed, have sufficient column density to form CO.
% unresolved CO?detected molecular clouds in other galaxies should have an average A_V = 4 mag.

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCs identified in the accretion phase of \flower in our simulation (star symbols) 
compared to observational data of molecular clouds in the Milky Way associated with massive \SF 
(magenta circles, green stars, blue dots, and black triangles) and empirical relations 
established based on \obs of the Milky Way.
Star symbols are color-coded by increasing $n_{\rm cut}$.
Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
% \citep{Lombardi10a}.
\label{fig:MR}}
\end{figure*}

>>>>

We show in \Fig{MR} the size-mass relation of the MCs of \flower in its accretion phase (see \Sec{sfh})
compared to 
observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF 
\citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on 
Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$.
\citet{Kauffmann10c} interpret this empirical relation 
as the threshold for massive \SF.
The implication of this result is that cluster-forming cloud fragments are 
found to be more massive than those that are devoid of clusters 
at a given radius. 
We also show the loci of constant surface densities in \Fig{MR}, parameterized through the visual extinction $A_V$.

As shown in \Fig{MR}, the MCs identified in the accretion phase of \flower lie above this relation, along the locus 
with a visual extinction of $A_V$\eq4\,mag \citep{Lombardi10a}, which 
% {\AP note that we can directly calculate Av given the dust properties in the galaxy or approximate it as av = cost N * Z con cost assuming a MW-like scaling}
is below the locus of $A_V$\eq100\,mag followed by Milky Way clouds.
This can be understood by acknowledging the fact that a H$_2$ molecular cloud 
does not necessary contain CO (e.g., as CO forms deeper in molecular clouds),
and that our simulation does not have enough resolution to directly form CO\footnote{
In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we 
model the internal structure of MC within each cell in our simulation.}.
That is, the MCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the 
fact that the MCs in our simulation have lower column densities than the star-forming cores observed in the Milky Way, which are 
observationally well-resolved within an MC, and indeed, have sufficient column density to form CO.

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCs identified in the accretion phase of \flower in our simulation (star symbols) 
compared to observational data of molecular clouds in the Milky Way associated with massive \SF 
(magenta circles, green stars, blue dots, and black triangles) and empirical relations 
established based on \obs of the Milky Way.
Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
Star symbols are color-coded by increasing $n_{\rm cut}$.
Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
The colored lines show the loci expected for various visual extinctions ($A_V$), which corresponds to 
lines of constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
\label{fig:MR}}
\end{figure*}
